Characterizing subarctic biomes for land surface modeling of pollution and climate risk

### 2021-05-09 supplements/VegOzone_supplement.tex
Remove figures

\begin{figure*}[t]
  \includegraphics[width=12cm]{test_fennoscandia}
  \caption{Maximum daily sun shine duration based on geometrical calculations at different sites in Fennoscandia. Midnight sun conditions at Jergul/Karasjok and Svanvik prevail from the end of May until the end of July, while at Esrange and Pallas they only prevail from the beginning of June until mid of July.}
  \label{fig:sunlight_fennoscandia}
\end{figure*}

\begin{figure*}[t]
  \includegraphics[width=12cm]{ozone_climatology_fenoscandic_obs}
  \caption{Multi-annual mean of daily mean ozone at observation sites in Fennoscandia. The large spread in case of Svanvik and Janiskoski is due to the lower statistics. All climatologies peak in spring, with peak values in April. The annual average ozone concentration \chem{\left<[O_3]\right>} at Svanvik is $6.6\,\unit{ppb}$ lower than at the sites at Jergul/Karasjok (NOR), Esrange (SWE), and Pallas (FIN).}
  \label{fig:ozone_climatology_fenoscandic_obs}
\end{figure*}

>>>>

%\begin{figure*}[t]
%  \includegraphics[width=12cm]{test_fennoscandia}
%  \caption{Maximum daily sun shine duration based on geometrical calculations at different sites in Fennoscandia. Midnight sun conditions at Jergul/Karasjok and Svanvik prevail from the end of May until the end of July, while at Esrange and Pallas they only prevail from the beginning of June until mid of July.}
%  \label{fig:sunlight_fennoscandia}
%\end{figure*}

%\begin{figure*}[t]
%  \includegraphics[width=12cm]{ozone_climatology_fenoscandic_obs}
%  \caption{Multi-annual mean of daily mean ozone at observation sites in Fennoscandia. The large spread in case of Svanvik and Janiskoski is due to the lower statistics. All climatologies peak in spring, with peak values in April. The annual average ozone concentration \chem{\left<[O_3]\right>} at Svanvik is $6.6\,\unit{ppb}$ lower than at the sites at Jergul/Karasjok (NOR), Esrange (SWE), and Pallas (FIN).}
%  \label{fig:ozone_climatology_fenoscandic_obs}
%\end{figure*}
